Human capital mediates natural selection in contemporary humans

### 2022-05-17 why-natural-selection.Rmd
update van alten citation

Figure \@ref(fig:plot-res-wt) plots selection effects in the whole
sample.[^balance-diverse-def] To correct for ascertainment bias, we use
participant weights from @van2021effects, which match the UK Biobank eligible
population on sex, birth year, location, education, employment, health,
household size and tenure, number of cars and age at death. Weighting makes a
large difference: effect sizes go up by a mean of 
`r scales::percent(mean_rel$Main - 1)`.[^weighting] `r n_sig` out of 33 weighted
selection effects are significant at $p$ < 0.05/33.

@@

Weighting data was kindly provided by @van2021effects.

>>>>

Figure \@ref(fig:plot-res-wt) plots selection effects in the whole
sample.[^balance-diverse-def] To correct for ascertainment bias, we use
participant weights from @vanalten2022reweighting, which match the UK Biobank eligible
population on sex, birth year, location, education, employment, health,
household size and tenure, number of cars and age at death. Weighting makes a
large difference: effect sizes go up by a mean of 
`r scales::percent(mean_rel$Main - 1)`.[^weighting] `r n_sig` out of 33 weighted
selection effects are significant at $p$ < 0.05/33.

@@

Weighting data was kindly provided by @vanalten2022reweighting.
